\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{10}


\bibitem{1P}
E. Allier, J. Goulier, G. Sicard, A. Dezzani, E. Andre and M. Renaudin, "A 120nm low power asynchronous ADC," \emph {International Symposium on Low Power Electronics and Design}, 2005.

\bibitem{2P}
F. Akopyan, R. Manohar, and A. B. Apsel, "A level-crossing flash asynchronous analog-to-digital converter," \emph {International Symposium on Asynchronous Circuits and Systems}, 2006.

\bibitem{7P}
E. Allier, G. Sicard, L. Fesquet and M. Renaudin, "Asynchronous level crossing analog to digital converters," \emph {Elsevier Journal of the International Measurement Confederation}, 2005.

\bibitem{8P}
A. Fayed and M. Ismail, "A High Speed, Low Voltage CMOS Offset Comparator," \emph {Analog Integrated Circuits and Signal Processing}, 2003.

\bibitem{9P}
 Daegyu Lee, Jincheol Yoo, Kyusun Choi and J. Ghaznavi, "Fat tree encoder design for ultra-high speed flash A/D converters," \emph { Midwest Symposium on Circuits and Systems}, 2002.


\bibitem{3P}
R. Agarwal, M. Trakimas and S. Sonkusale, "Adaptive asynchronous analog to digital conversion for compressed biomedical sensing," \emph {IEEE Conference on Biomedical Circuits and Systems}, 2009.

\bibitem{4P}
M. Trakimas, S. Sonkusale,  "A 0.8 V asynchronous ADC for energy constrained sensing applications," \emph {IEEE Conference on Custom Integrated Circuits Conference}, 2008.

\bibitem{5P}
S. W. Michael and R. W. Brodersen "A 6-bit 600-MS/s 5.3-mW Asynchronous ADC in 0.13$\mu$m CMOS," \emph {IEEE Journal of Solid-State Circuits}, 2006.

\bibitem{6P}
Ying-Zu Lin, Soon-Jyh Chang, Yen-Ting Liu, Chun-Cheng Liu and Guan-Ying Huang, "An Asynchronous Binary-Search ADC Architecture With a Reduced Comparator Count," \emph {IEEE Transactions on Circuits and Systems}, 2010.

\bibitem{1L}
B. Murmann, "ADC Performance Survey 1997-2010," [Online]. Available: $http://www.stanford.edu/~murmann/adcsurvey.html$.

\end{thebibliography}
