\begin{center}
\abstract
\end{center}

\par
\hspace{0.5cm} Due to the increasing importance of products like laptops, music players, cell phones and implantable bio-medical products which are operated using batteries, it has became imperative to prolong the battery life as much as possible to achieve high performance. No significant improvements have been made in the energy density of commonly available batteries from many years. All batteries are limited to a maximum amount of energy per unit volume. The bigger the battery compartment, the longer the battery will last. On the other hand, advancements in CMOS technology is much faster than compared to the advancements in battery technology. By doubling the number of transistors on a chip for every two years, the battery technology is not sufficient to provide required power for the chips to attain an optimum performance. Hence, power reduction is an important and challenging target for these type of products.

\par
\hspace{0.5cm} Generally most of the real time signals are in analog form, for example sound generated vocally from human beings, bio-medical signals like electroencephalograph, electrocardiograph. Also, human beings perceive and retain information in analog form. Analog processing of these signals is very difficult because of the noise interference. Hence, Digital Signal Processing is used to process these signals because they are less prone to noise interference and advanced Digital Signal Processing algorithms made signal processing easy in digital domain. So, to convert these analog signals into digital signals analog-to-digital converters are used and similarly digital-to-analog converters are used to convert digital signals into analog signals for further processing. Systems like bio-chips which are implanted in the human body should consume very less power, at the same time we have to maintain its performance. Hence, it is quite challenging to come up with a low power and high speed analog-to-digital and digital-to-analog converters. In both these converters resolution, speed and power consumptions are most important features.

\par
\hspace{0.5cm} Importance of battery run systems continues to grow day by day. Traditional approaches to designing these systems vary from typical semiconductor design. Every low power design is different and will have its own interesting set of problems to solve. We have to think through every element of the design if we want to operate at low power levels. Some of important issues are to consider include power consumption limits, speed and size restrictions. Speed is one of the most important problem in low power design. Increase in speed results in higher power consumption. Similarly increase in area of the chip also results increase in power consumption. In this work an attempt has been made to design an analog-to-digital converter which consumes low power in applications where the signal should be monitored continuously and vary brief amount of time like pressure controller and flow controls etc.
